Experiment

### 2019-05-04 analysis/experiment.Rmd
Add new questions

orgs <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
issues <- c("Emergency response", "Environment", "Human rights", "Refugee relief")
orgal_practices <- c("Financial transparency", "Accountability")
funding <- c("Many small private donations", "Handful of wealthy private donors", "Government grants")
govt <- c("Friendly relationship", "Criticized", "Under crackdown")

tribble(
  ~Attribute, ~`Option 1`, ~`Option 2`, ~`Option 3`, ~None,
  "Organization", sample(orgs, 1), sample(orgs, 1), sample(orgs, 1), "—",
  "Issue area", sample(issues, 1), sample(issues, 1), sample(issues, 1), "—",
  "Organizational practices", sample(orgal_practices, 1), sample(orgal_practices, 1), sample(orgal_practices, 1), "—",
  "Funding sources", sample(funding, 1), sample(funding, 1), sample(funding, 1), "—",
  "Relationship with host government", sample(govt, 1), sample(govt, 1), sample(govt, 1), "—"
) %>% 
  mutate(Attribute = pandoc.strong.return(Attribute)) %>% 
  pandoc.table(justify = "lcccc", split.tables = Inf)
```

>>>>

orgs <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
issues <- c("Emergency response", "Environment", "Human rights", "Refugee relief")
transparency <- c("Engages in transparency", "Doesn't engage in transparency")
accountability <- c("Engages in accountability", "Doesn't engage in accountability")
funding <- c("Many small private donations", "Handful of wealthy private donors", "Government grants")
govt <- c("Friendly relationship", "Criticized", "Under crackdown")

tribble(
  ~Attribute, ~`Option 1`, ~`Option 2`, ~`Option 3`, ~None,
  "Organization", sample(orgs, 1), sample(orgs, 1), sample(orgs, 1), "—",
  "Issue area", sample(issues, 1), sample(issues, 1), sample(issues, 1), "—",
  "Transparency", sample(transparency, 1), sample(transparency, 1), sample(transparency, 1), "—",
  "Accountability", sample(accountability, 1), sample(accountability, 1), sample(accountability, 1), "—",
  "Funding sources", sample(funding, 1), sample(funding, 1), sample(funding, 1), "—",
  "Relationship with host government", sample(govt, 1), sample(govt, 1), sample(govt, 1), "—"
) %>% 
  mutate(Attribute = pandoc.strong.return(Attribute)) %>% 
  pandoc.table(justify = "lcccc", split.tables = Inf)
```
